hbm_paper_results

### 2024-02-23 paper_main_results.Rmd
drop reference site configs

  # Bind the data to the combined dataframe
  combined_preds <- bind_rows(combined_preds, data)
}
```

@@

diffs.df <- fread(file = raw_files, sep=",") %>%
     mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|-", "", Source_File))
```

@@

subj_sum.df <- fread(file = raw_files, sep=",") %>%
     mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|-", "", Source_File))
```

@@

combined_var <- inner_join(combined_var, plot.info)
```

@@

# p_diff_annotate <- annotate_figure(p_diff)
# p_diff_annotate
```
plot w ref sites
```{r, eval=FALSE}
#get means w/in feature 
mean.cent.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno, pheno_abs.diff.list) %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss", "cf.lm_refA", "cf.gam_refA", "cf.gamlss_refA"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="cent_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  # mutate(pheno=gsub(".z", "", pheno)) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

mean.cent.diffs.long %>%
  dplyr::filter(dataset != "ukb_CN") %>%
  ggplot() +
  geom_histogram(aes(x=cent_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_grid(dataset~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  labs(y="Percent Features", x = "Mean Absolute Centile Error") +
  ggtitle("Absolute errors in centiles of brain structure features across ComBat processing pipelines")
```
Quick comp of cf.gam and cf.gamlss

@@

gam_better$pheno

>>>>

  # Bind the data to the combined dataframe
  combined_preds <- bind_rows(combined_preds, data)
}

#drop refA sites, not using for these analyses
combined_preds <- combined_preds %>%
  dplyr::filter(!grepl('_refA', dataset)) #drop refA levels
```

@@

diffs.df <- fread(file = raw_files, sep=",") %>%
     mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|-", "", Source_File))

#drop refA sites, not using for these analyses
diffs.df <- diffs.df %>%
  dplyr::filter(!grepl('_refA', dataset)) #drop refA levels
```

@@

subj_sum.df <- fread(file = raw_files, sep=",") %>%
     mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|-", "", Source_File))

#drop refA sites, not using for these analyses
subj_sum.df <- subj_sum.df %>%
  dplyr::filter(!grepl('_refA', dataset)) #drop refA levels
```

@@

combined_var <- inner_join(combined_var, plot.info)

#drop refA sites, not using for these analyses
combined_var <- combined_var %>%
  dplyr::filter(!grepl('_refA', dataset)) #drop refA levels
```

@@

# p_diff_annotate <- annotate_figure(p_diff)
# p_diff_annotate
```

@@
